Higher-Order unification for free!

### 2024-04-25 paper/main.tex
fix typos

In the literature we could find a related encoding of the Calculus of
Constructions (CC)~\cite{felty93lics}. The goal of that work is to exhibit
a logic program performing proof checking for CC and hence relate the
proof system of intuitionistic higher-order logic (that animates $\lambda$Prolog
programs) with the one of CC. The encoding is hence tailored
toward a different goal, for example it utilizes three relations to represent the
equational theory of CC, and that choice alone makes things harder for us.
Section 6 contains a discussion about the use of the
unification procedure of the meta language in presence of non ground goals, but
the authors are not interested in exploiting a decidable fragment of
higher-order unification but are reather leaning towards an interactive
system where explicit
control is given the user.

>>>>

In the literature we could find a related encoding of the Calculus of
Constructions (CC)~\cite{felty93lics}. The goal of that work is to exhibit
a logic program performing proof checking for CC and hence relate the
proof system of intuitionistic higher-order logic (that animates $\lambda$Prolog
programs) with the one of CC. The encoding is hence tailored
toward a different goal, for example it utilizes three relations to represent the
equational theory of CC, and that choice alone makes things harder for us.
Section 6 contains a discussion about the use of the
unification procedure of the meta language in presence of non ground goals, but
the authors are not interested in exploiting a decidable fragment of
higher-order unification but are reather leaning towards an interactive
system where the user is given
control over the search procedure.
